Conference Paper Title\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-03-11 paper/paper.tex
added more paragraphs, created a table in latex

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. 
Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these 
computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the 
new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network 
and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par
\section{Previous Work}
There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
In these citation networks, in particular, node classification and link prediction have been heavily explored. 
In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
71 different papers done on node classification of the Cora dataset.  \par

@@

>>>>

\title{Conference Paper Title\\
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

In particular, machine learning hardware is a new field that has skyrocketed from the recent popularity of machine learning. 
Due to the compute-intensive nature of this field, plenty of research exists in the hardware infrastructure to support these 
computing loads. We utilize GNNs for node classification and link prediction to explore existing datasets and comment on the 
new corpus of machine learning hardware papers. The main challenges are processing data for useful representations of the network 
and data interpretation on the created GNNs to comment on the field of machine learning hardware. \par

\section{Previous Work}
There have been many previous explorations of citation networks using the datasets Cora, Citeseer, and PubMed Diabetes. 
In these citation networks, in particular, node classification and link prediction have been heavily explored. 
In Optimization of Graph Neural Networks with Natural Gradient Descent, Izadi et al improve on traditional optimization 
algorithms such as ADAM and stochastic gradient descent (SGD), producing a superior accuracy (90.16±0.59\%) 
by utilizing a proposed method inspired by natural gradient descent [1]. This paper achieved the highest accuracy across 
71 different papers done on node classification of the Cora dataset.  \par

@@

After applying these operations, the total number of nodes increases from 2,605 to 9,605 after removing 
unusable nodes. This graph also has 52,945 edges and 6,821 features, from applying the 
same methods of keyword extraction. When increasing the size of the dataset, we were also 
met with a class imbalance - there were far fewer papers in ML Accelerators in the WoS database, 
less than two thousand papers, while the other categories had over five thousand papers each. 
In this regard, we can infer that ML accelerators are less popular (or at least less explored) 
than other papers. However, since WoS is our only source of data, this could also result from 
a lack of these papers in the Web of Science database. Since class imbalances can also impact 
performance on ML models, this also acts as a limitation on the GNN models in use. \par

Recognizing that the number of features is nearly double that of any of the given datasets, 
this can also lead to excessive computation time and increased bias in the results from 
features that supply noise in the machine learning models. So, we then apply principal 
component analysis (PCA) to these features to select the features that best describe the 
classifications and links between each node. Here, we apply PCA with an explained variance 
of 80\% to provide a sufficient level of specificity without overfitting the data, 
reducing the number of features to 760. \par

Following this, we also update the characteristics of our graph, producing an average 
degree of 11.09, an average clustering coefficient of 0.158, and a diameter of 18. 
From the differences in these datasets, we see that the average degree of our dataset 
is much higher than the given datasets. However, the clustering coefficient and diameter 
of the dataset are comparable to those of other datasets. These metrics are compared to 
the other datasets in Table 1 below. \par

From this table, we can see differences among the datasets explored in this paper, 
revealing the structural properties of these different graphs. Primarily, there are 
many more edges in the updated WoS compared to the other datasets, resulting in a much 
higher average degree for the updated dataset. However, the clustering coefficient for 
our dataset is still comparable to other datasets, implying that the field of machine 
learning hardware tends to have a significant number of citations, but a similar number 
of these papers forming a well-defined cluster. While Cora and CiteSeer are most similar 
to the WoS database in terms of content, both relating to machine learning, the graph 
characteristics of WoS are most similar to PubMed, with a higher degree and lower 
clustering coefficient. However, another limitation of utilizing WoS as our primary 
database is that it is unclear whether these characteristics arise as a quality of 
the database or as a characteristic of the field of ML hardware in general. \par

\begin{table}[htbp]
    \caption{Citation Network Characteristics}
    \begin{center}
        \begin{tabular}{|c|cccccc|}
        \hline
        % \textbf{Table}&\multicolumn{6}{|c|}{\textbf{Table Column Head}} \\
        % \cline{1-4} 
        \textbf{} & \textbf{\textit{Nodes}} & \textbf{\textit{Edges}} & \textbf{\textit{Features}} &
        \textbf{\textit{Degree}} & \textbf{\textit{CC$^{\mathrm{a}}$}} & \textbf{\textit{MD$^{\mathrm{b}}$}} \\
        \hline
        \textbf{\textit{Cora}} & 
        2708& 5429& 1433& 3.89807& 0.24067& 19 \\
        \textbf{\textit{CiteSeer}} & 
        3312& 4660& 3704& 2.81400& 0.14255& 28 \\
        \textbf{\textit{Pubmed}} & 
        19717& 44348& 500& 4.49632& 0.06017& 18 \\
        \textbf{\textit{Small WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \textbf{\textit{Large WoS}} & 
        2605& 6600& 4134& 5.06717& 0.13529& 16 \\
        \hline
        \end{tabular}
        \label{tab1}
        {$^{\mathrm{a}}$Clustering Coefficient.}
        {$^{\mathrm{b}}$Maximum Diameter.}
    \end{center}
\end{table}
